### 2021-11-28 README.Rmd
update read me

# Evaluating Informative Hypotheses With Equality and Inequality Constraint: The Bayes Factor Encompassing Prior Approach

In this repository we collect all the materials of the study “*Evaluating Informative Hypotheses With Equality and Inequality Constraint: The Bayes Factor Encompassing Prior Approach*”. The aim of the paper is to provide a clear and detailed description of the Bayes Factor with the encompassing prior approach considering an applied example regarding attachment theory.

@@

To guarantee the reproducibility of the results, the R-package`drake` is used to manage the analysis workflow and to enhance the readability and transparency of the analysis. To know more about `drake` consider the [official Git-hub page](https://github.com/ropensci/drake) or the [user manual](https://books.ropensci.org/drake/). Summarizing, using `drake` the user defines the plan of the analysis where each step in the analysis is defined trough functions. Functions can be appropriately defined to obtain desired targets (i.e., R-output with results of interests) and they are declared in another script. Subsequently, `drake` manages the whole analysis recognizing the dependency structure of the different targets. When any change is made to the code `drake` evaluates the analysis and updates the results. Following the *functional programming paradigm* (i.e., defining functions for each step of the analysis), it allows us to avoid "*coping and paste*" in the code, it makes debugging easier, and it facilitates the reading of the code.

Moreover, the R-package `renv` is used to manage the dependencies of the R-packages used in the analysis. The `renv` package allows to create an isolated, portable, and reproducible environment where the analyses are run. To know more about `renv` consider the [official documentation](https://rstudio.github.io/renv/articles/renv.html). However, `renv` is limited as it can not handle different R versions.

@@

1. Download the the repository on your local machine
    ```{bash, eval = FALSE}
    git clone https://github.com/ClaudioZandonella/Attachment
    ```
1. Open the R project by double-clicking the file `Attachment.Rproj` you can find in the project main directory. A new R-studio session will open.
1. Run `renv::restore()` to install project's dependencies (have a coffee, it takes some time).
1. Now the required package will be loaded. Restart the R session (`command`/`ctrl` + `shift` + `f10`) so `devtools::load_all()` is automatically run (according to `.Rprofile`) to load all functions used in the analysis defined in the `R/` folder.

    > Note that also `source("Documents/Utils_report.R")` is automatically run to load report utilities functions (functions to load analysis results and to compile the bookdown).

1. Open `Analysis/Analysis_Drake.R` and run each line (one by one) to run the analysis using drake. First, the analysis environment is setted together with the analysis plan (available at `R/Plan.R`). Next the analysis targets are computed (have a coffee, it takes a long time). Finally, the analysis results are loaded and briefly presented.

    > Note that you can access the analysis targets with using the functions `drake::loadd(<name_target>)`, or load all the results with `drake_load_all()`.

    > It could happen that some times the session session stay idle when fitting `brms` models without throwing errors. In this case, it is necessary to force restarting the R session and rerun the analysis. An error warning message will appear `Error: drake's cache is locked`. Just follow the instructions provided by drake to force unlock of the cache  `drake::drake_cache("...")$unlock()`.

@@

To run the analysis in a Docker container, build the image according to the `Dockerfile` present in the project main directory, using
```{bash, eval = FALSE}
docker build -t attachment .
```

> It is important too build the image before to run the analysis

>>>>

# Evaluating Informative Hypotheses with Equality and Inequality Constraints:\\ A Tutorial Using the Bayes Factor via the Encompassing Prior Approach

In this repository we collect all the materials of the study “*Evaluating informative hypotheses with equality and inequality constraints: A tutorial using the Bayes factor via the encompassing prior approach*”. The paper aims to provide a clear and detailed description of the Bayes factor with the encompassing prior approach considering an applied example regarding attachment theory.

@@

To guarantee the reproducibility of the results, the R-package`drake` is used to manage the analysis workflow and to enhance the readability and transparency of the analysis. To know more about `drake` consider the [official Git-hub page](https://github.com/ropensci/drake) or the [user manual](https://books.ropensci.org/drake/). Summarizing, using `drake` the user defines the plan of the analysis where each step in the analysis is defined through functions. Functions can be appropriately defined to obtain desired targets (i.e., R-output with results of interests) and they are declared in another script. Subsequently, `drake` manages the whole analysis recognizing the dependency structure of the different targets. When any change is made to the code `drake` evaluates the analysis and updates the results. Following the *functional programming paradigm* (i.e., defining functions for each step of the analysis) allows us to avoid "*coping and paste*" in the code, it makes debugging easier, and it facilitates the reading of the code.

Moreover, the R-package `renv` is used to manage the dependencies of the R-packages used in the analysis. The `renv` package allows the creation of an isolated, portable, and reproducible environment where the analyses are run. To know more about `renv` consider the [official documentation](https://rstudio.github.io/renv/articles/renv.html). However, `renv` is limited as it can not handle different R versions.

@@

1. Download the repository on your local machine
    ```{bash, eval = FALSE}
    git clone https://github.com/ClaudioZandonella/Attachment
    ```
1. Open the R project by double-clicking the file `Attachment.Rproj` you can find in the project main directory. A new R-studio session will open.
1. Run `renv::restore()` to install the project's dependencies (have a coffee, it takes some time).
1. Now the required package will be loaded. Restart the R session (`command`/`ctrl` + `shift` + `f10`) so `devtools::load_all()` is automatically run (according to `.Rprofile`) to load all functions used in the analysis defined in the `R/` folder.

    > Note that also `source("Documents/Utils_report.R")` is automatically run to load report utility functions (functions to load analysis results and to compile the bookdown).

1. Open `Analysis/Analysis_Drake.R` and run each line (one by one) to run the analysis using drake. First, the analysis environment is set together with the analysis plan (available at `R/Plan.R`). Next, the analysis targets are computed (have a coffee, it takes a long time). Finally, the analysis results are loaded and briefly presented.

    > Note that you can access the analysis targets using the functions `drake::loadd(<name_target>)`, or load all the results with `drake_load_all()`.

    > It could happen that sometimes the session stays idle when fitting `brms` models without throwing errors. In this case, it is necessary to force restarting the R session and rerun the analysis. An error warning message will appear: `Error: drake's cache is locked`. Just follow the instructions provided by drake to force unlock of the cache  `drake::drake_cache("...")$unlock()`.

@@

To run the analysis in a Docker container, first, download the repository on your local machine. Next, build the image according to the `Dockerfile` present in the project main directory, using
```{bash, eval = FALSE}
docker build -t attachment .
```

> It is important to build the image before running the analysis
